Figures

### 2019-04-24 figures/02_hierarchical_demo.Rmd
linting
use library calls from utils script

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
```

```{r hu4_n, echo=FALSE, message=TRUE, eval=TRUE}
library(dplyr)
library(LAGOSNEgis)
library(sf)
library(ggplot2)
library(cowplot)
library(classInt)

# setwd("figures")
ids <- test <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
source("../scripts/99_utils.R")
```

```{r hu4_n, echo=FALSE, message=TRUE, eval=TRUE}
# setwd("figures")
ids <- test <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()
